cardinalR: Generating interesting high-dimensional data structures

### 2025-05-06 paper-cardinalR.Rmd
Added gen_curvycylinder

>>>>

The `gen_curvycylinder(n, p, h)` function generates a $p$-dimensional dataset of $n$ observations structured as a $3\text{-}D$ cylindrical manifold with an added nonlinear curvy dimension, and optional noise dimensions when $p > 4$.

The core structure consists of a circular base and height values, extended by a nonlinear fourth dimension:

Let $\theta \sim \mathcal{U}(0, 3\pi)$ represent a random angle on a circular base and $z \sim \mathcal{U}(0, h)$ represent the height along the cylinder.

The coordinates are defined as:

* $X_1 = \cos(\theta)$ (Circular base, x-axis),
* $X_2 = \sin(\theta)$ (Circular base, y-axis),
* $X_3 = z$ (Linear height),
* $X_4 = \sin(z)$ (Nonlinear curvy variation along height).

This forms a curvy cylindrical surface in $4\text{-}D$, where the fourth dimension bends periodically along the height axis, resembling a helicoid or twisting wave along the cylinder.

For $p > 4$, dimensions $X_5$ through $X_p$ are generated as:

$$
X_j \sim \mathcal{N}(0, 0.05^2)$,\text{ for }$j = 5, \ldots, p.
$$

These dimensions represent unstructured, low-variance noise.
